Motional Ground State Cooling Outside the Lamb-Dicke Regime

### 2018-01-30 paper.tex
Fix plot
Add dashed line for imaging survival
Remove mentioning of 96% imaging survival in the text and move it to the caption

\begin{abstract}
  We report Raman sideband cooling of a single sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite a large Lamb-Dicke parameter, high initial temperature, and
  large differential light shifts between the excited state and the ground state,
  we achieve a ground state population of $93.5(7)$\% after $53$ ms of cooling,
  for the 96\% of atoms that survive re-imaging. %% survives the first image?
  Our technique includes addressing high-order sidebands,
  where several motional quanta are removed by a single laser pulse, and
  fast modulation of the optical tweezer intensity.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is possible,
  even without tight confinement and low initial temperature.
\end{abstract}

@@

\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_r.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_p1.pdf}
  \caption{(A,B) Left to right: Radial Raman sideband spectrum of $\Delta n=1,\,\Delta n=0,\,\Delta n=-1,\,\Delta n=-2$ before and after Raman sideband cooling for $x$ and $y$ axis.
    (C,D) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid lines in (C) and (D) are fits to a Rabi-flopping
    that includes a thermal distribution of motional states~\cite{Meekhof1996}
    as well as off-resonant scattering from the Raman beams.
    The blue lines correspond to a 1D ground state probability of $98.1$\% after cooling
    and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_az.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_p1.pdf}
  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-5$
    before and after Raman sideband cooling.
    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
    are fits to the Rabi flopping and yield a ground state probability of $95$\%
    after cooling and
    the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The green line in (C), includes the additional decoherence due to
    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
    We see that the decoherence effect is strongest for the post-cooling data on
    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
    \label{f-axial}}
\end{figure*}

@@

Combining the axial and radial cooling results,
a single Na atom is in the 3D ground state with a probability of 93.5(7)\% after RSC.
We note that there is an additional 4\% population loss from imaging.
The cooling efficiency is limited by spontaneous scattering rate
(0.1-0.2 kHz) from the Raman beams,
as well as spectral broadening from magnetic field fluctuations.

@@

%% TODO
% Plot marker
% Remove plot title
% Remove mention of imaging loss in the text and move it to the figure caption
% Add 96% survival line.
% 94(1) ?

>>>>

\begin{abstract}
  We report Raman sideband cooling of a single sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite a large Lamb-Dicke parameter, high initial temperature, and
  large differential light shifts between the excited state and the ground state,
  we achieve a ground state population of $93.5(7)$\% after $53$ ms of cooling.
  Our technique includes addressing high-order sidebands,
  where several motional quanta are removed by a single laser pulse, and
  fast modulation of the optical tweezer intensity.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is possible,
  even without tight confinement and low initial temperature.
\end{abstract}

@@

\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_r.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_p1.pdf}
  \caption{(A,B) Left to right: Radial Raman sideband spectrum of $\Delta n=1,\,\Delta n=0,\,\Delta n=-1,\,\Delta n=-2$ before and after Raman sideband cooling for $x$ and $y$ axis.
    (C,D) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid lines in (C) and (D) are fits to a Rabi-flopping
    that includes a thermal distribution of motional states~\cite{Meekhof1996}
    as well as off-resonant scattering from the Raman beams.
    The blue lines correspond to a 1D ground state probability of $98.1$\% after cooling
    and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The horizontal dashed line in the plot corresponds to the $96\%$ survival probability
    after the first image.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_az.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_p1.pdf}
  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-5$
    before and after Raman sideband cooling.
    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
    are fits to the Rabi flopping and yield a ground state probability of $95$\%
    after cooling and
    the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The green line in (C), includes the additional decoherence due to
    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
    We see that the decoherence effect is strongest for the post-cooling data on
    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
    \label{f-axial}}
\end{figure*}

@@

Combining the axial and radial cooling results,
a single Na atom is in the 3D ground state with a probability of 93.5(7)\% after RSC.
The cooling efficiency is limited by spontaneous scattering rate
(0.1-0.2 kHz) from the Raman beams,
as well as spectral broadening from magnetic field fluctuations.

@@
